
\begin{thebibliography}{}
\bibitem{RapiTime} 
  https://www.rapitasystems.com/
  Last accessed May 15, 2018.
 
\bibitem{Drops} 
  Deverge, Jean-François, and Isabelle Puaut. ``Safe measurement-based WCET estimation.'' In OASIcs-OpenAccess Series in Informatics, vol. 1. Schloss Dagstuhl-Leibniz-Zentrum für Informatik, 2007.  

\bibitem{Wenzel} 
  Wenzel, Ingomar, Raimund Kirner, Bernhard Rieder, and Peter Puschner. ``Measurement-based worst-case execution time analysis.'' In Software Technologies for Future Embedded and Ubiquitous Systems, 2005. SEUS 2005. Third IEEE Workshop on, pp. 7-10. IEEE, 2005.
  
\bibitem{AIT}
  https://www.absint.com/index.htm
  Last accessed May 15, 2018.

\bibitem{BoundT}
  http://www.bound-t.com/
  Last accessed May 15, 2018.
  
\bibitem{Chronos}
  Li, Xianfeng, Yun Liang, Tulika Mitra, and Abhik Roychoudhury. ``Chronos: A timing analyzer for embedded software.'' Science of Computer Programming 69, no. 1-3 (2007): 56-67.

\bibitem{Survey}
  Wilhelm, Reinhard, Jakob Engblom, Andreas Ermedahl, Niklas Holsti, Stephan Thesing, David Whalley, Guillem Bernat et al. ``The worst-case execution-time problem—overview of methods and survey of tools.'' ACM Transactions on Embedded Computing Systems (TECS) 7, no. 3 (2008): 36.
  
\bibitem{AIT2}
  Wilhelm, Reinhard. ``Determining Bounds on Execution Times.'' Embedded Systems Handbook 2 (2005).

\bibitem{Loop}
  Misailovic, Sasa, Stelios Sidiroglou, Henry Hoffmann, and Martin Rinard. ``Quality of service profiling.'' In Proceedings of the 32nd ACM/IEEE International Conference on Software Engineering-Volume 1, pp. 25-34. ACM, 2010.

\bibitem{Green}
  Baek, Woongki, and Trishul M. Chilimbi. ``Green: a framework for supporting energy-conscious programming using controlled approximation.'' In ACM Sigplan Notices, vol. 45, no. 6, pp. 198-209. ACM, 2010.

\bibitem{Knobs}
  Hoffmann, Henry, Stelios Sidiroglou, Michael Carbin, Sasa Misailovic, Anant Agarwal, and Martin Rinard. ``Dynamic knobs for responsive power-aware computing.'' In ACM SIGPLAN Notices, vol. 46, no. 3, pp. 199-212. ACM, 2011.

\bibitem{Image}
  Lou, Liming, Paul Nguyen, Jason Lawrence, and Connelly Barnes. ``Image Perforation: Automatically Accelerating Image Pipelines by Intelligently Skipping Samples.'' ACM Transactions on Graphics (TOG) 35, no. 5 (2016): 153.

\bibitem{Canary}
  Laurenzano, Michael A., Parker Hill, Mehrzad Samadi, Scott Mahlke, Jason Mars, and Lingjia Tang. ``Input responsiveness: using canary inputs to dynamically steer approximation.'' ACM SIGPLAN Notices 51, no. 6 (2016): 161-176.

\bibitem{Taclebench}
  Falk, Heiko, Sebastian Altmeyer, Peter Hellinckx, Björn Lisper, Wolfgang Puffitsch, Christine Rochange, Martin Schoeberl, Rasmus Bo Sørensen, Peter Wägemann, and Simon Wegener. ``TACLeBench: A benchmark collection to support worst-case execution time research.'' In OASIcs-OpenAccess Series in Informatics, vol. 55. Schloss Dagstuhl-Leibniz-Zentrum fuer Informatik, 2016.
  
\bibitem{Patmos}
  Schoeberl, Martin, Pascal Schleuniger, Wolfgang Puffitsch, Florian Brandner, Christian W. Probst, Sven Karlsson, and Tommy Thorn. ``Towards a time-predictable dual-issue microprocessor: The Patmos approach.'' In Bringing Theory to Practice: Predictability and Performance in Embedded Systems, vol. 18, pp. 11-21. 2011.

\bibitem{tcrest}
  http://www.t-crest.org/
  Last accessed May 16, 2018.

\bibitem{gtcrest}
  https://github.com/t-crest
  Last accessed May 16, 2018.
  
\end{thebibliography}
